---
title: "Problem set 3"
author: "Yanping Zhu"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
Github link: 
```{r setup, include=FALSE}
library(MatchIt)
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(zoo)
library(broom)
library(timereg)
library(plm)
library(lfe)
library(aTSA)

setwd('/Users/yanpingzhu/Desktop/Courses/BUSI 525 Topics in Financial Markets Research/Assignments/Problem set 1')
```
#Part 1—No Skilled Funds:

##Q1
```{r}
set.seed(2800)

N <- 1000
T <- 120

#generate market excess return and the error term
rmkt <- rnorm(n = N * T, mean = 0.05/12, sd = 0.2/sqrt(12))
eps  <- rnorm(n = N * T, mean = 0, sd = 0.1/sqrt(12))

#set id for each fund
nid = rep(1:N, each = T)



df_1 <- data.frame(nid = nid, rmkt, eps)

#assuming beta = 1 for all funds and alpha = 0 for all funds, generate the dependent variable 

df_1 <- df_1 %>% 
  mutate(r= 0 + rmkt + eps)
head(df_1)

#estimation for each fund
fit_per_fund <- dlply(df_1, "nid", function(df) lm(r ~ rmkt, data = df))

#extract the alphas and t-statistics
fitted <- ldply(fit_per_fund,tidy) %>% 
  filter(term == '(Intercept)')

head(fitted)

#number of funds that are skilled at 5\%
skilled <- fitted %>% 
  filter(p.value <= 0.05)
length(skilled$nid)

```

##Q2 

```{r}
hist(fitted$statistic, breaks=20, col="blue")
dtstat <- density(fitted$statistic)
plot(dtstat, main="Kernel Density of t-statistics")
polygon(dtstat, col="blue", border="black")


hist(fitted$p.value, breaks=20, col="blue")
dpval <- density(fitted$p.value)
plot(dpval, main="Kernel Density of p-values")
polygon(dpval, col="blue", border="black")


```

##Q3 

It looks like a uniform distribution. 



#Part 2—Some Skilled Funds:

For this part, I write a function with the parameter $\lambda$. The function first returns the plots of the cross-sectional distribution of estimated $\alpha$, t-stats and the p-values for each $\lambda$. 

Then it returns a vector of four values, with the first value being percentage of true positive, second being false positive, third being false negative, and the fourth being true negative. 

As we can see from the histograms of the fitted values, when lambda increases, the probability mass for small p-values, i.e., $p < 0.05$ increases. 

Here is the function.

```{r}

func <- function(lambda){

  #generate alpha for each fund
  alpha <- c(rep(0.05/12, lambda*N), rep(0, (1-lambda)*N))
  
  #since alpha does not vary with time
  alpha <- rep(alpha, each = T)

  #given that beta = 1 for all fund, we can generate the dependent variable 
  df_2 <- data.frame(nid = nid, alpha, rmkt, eps) %>% 
  mutate(r= alpha + rmkt + eps)
  
  #estimation for each fund
  fit_per_fund_2 <- dlply(df_2, "nid", function(df) lm(r ~ rmkt, data = df))

  fitted_2 <- ldply(fit_per_fund_2,tidy) %>% 
    filter(term == '(Intercept)')

  #make the plots for Q1 
  hist(fitted_2$estimate, breaks=15, col="blue")
  dest_2 <- density(fitted_2$estimate)
  plot(dest_2, main="Kernel Density of estimates")
  polygon(dest_2, col="blue", border="black")

  hist(fitted_2$statistic, breaks=15, col="blue")
  dtstat_2 <- density(fitted_2$statistic)
  plot(dtstat_2, main="Kernel Density of t-statistics")
  polygon(dtstat_2, col="blue", border="black")


  hist(fitted_2$p.value, breaks=25, col="blue")
  dpval_2 <- density(fitted_2$p.value)
  plot(dpval_2, main="Kernel Density of p-values")
  polygon(dpval_2, col="blue", border="black")
  

  #calculate the percentage of funds in four classifications 
  #combine data with true values of alphas and the estimated alphas
  data <- df_2 %>% 
    select(nid, alpha) %>% 
    unique() %>% 
    left_join(fitted_2 %>% select(nid, estimate, p.value), by = 'nid')
  
  #true positive
  tp <- data %>% 
    filter(p.value <= 0.05, alpha >0)
  Truepositive <- length(tp$nid)/1000

  #false positive
  fp <- data %>% 
    filter(p.value <= 0.05, alpha ==0)
  Falsepositive <- length(fp$nid)/1000

  #false negative
  fn <- data %>% 
    filter(p.value > 0.05, alpha >0)
  Falsenegative <- length(fn$nid)/1000

  #true negative
  tn <- data %>% 
    filter(p.value > 0.05, alpha ==0)
  Truenegative <- length(tn$nid)/1000

  
  percentages <- c(Truepositive, Falsepositive, Falsenegative, Truenegative)

  percentages


}
```


##Q1 and Q2

Now we look at the output of the function with $\lambda = 0.1, 0.25, 0.5,0.75$. 
```{r}
func(0.1)
func(0.25)
func(0.5)
func(0.75)
```


